### 2023-01-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@914afb2218a709c84b34774e733984514e44dffe 🚀

We then consider the output prediction from an arbitrary prediction
model, which is the probability \(p_{ij}\) that two species \(i\) and
\(j\) interact. To get an estimate of \(p_{ij}\) that accounts for
observation error, we resample the probability of each interaction
\(p_{ij}\) by simulating a set of several `particles,' where each
particle is a realization of an interaction occurring (either true or
false with probabilities \(p_{ij}\) and \(1-p_{ij}\) respectively) and
then being correctly observed with probabilities given by \(p_{fp}\) and
\(p_{fn}\) to yield a single boolean outcome for each particle.
(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Over many
samples of particles, the resulting frequency of `true' outcomes is a
single resample of the interaction probability \(p_{ij}^*\). Across
several samples each of several particles, this forms a distribution of
probabilities which are adjusted by the true and false negative rates.

@@

Why is this useful? For one, this analytic method avoids the extra
computation required by simulating samples from this distribution
directly. Further, it enables continuous extension of the number of
particles \(n_p\) as a uncertainty width. The natural analogue for the
number of particles sampled is the number of observations of
co-occurrence for a given pair of species---the fewer the particles, the
higher the variance of the resulting approximation. The normal
approximation is undefined for 0 particles (i.e.~0 observations
co-occurrence), although as \(n_p\) approaches 0 the approximated normal
(once truncated) approaches a uniform distribution on the interval
\((0,1)\), the maximum entropy distribution where we have no information
about the possibility of an interaction.

>>>>

We then consider the output prediction from an arbitrary prediction
model, which is the probability \(p_{ij}\) that two species \(i\) and
\(j\) interact. To get an estimate of \(p_{ij}\) that accounts for
observation error, we resample the probability of each interaction
\(p_{ij}\) by simulating a set of several `particles,' where each
particle is a realization of an interaction occurring (either true or
false with probabilities \(p_{ij}\) and \(1-p_{ij}\) respectively) and
then being correctly observed with probabilities given by \(p_{fp}\) and
\(p_{fn}\) to yield a single boolean outcome for each particle
(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Across of
many particles, the resulting frequency of `true' outcomes is a single
resample of the interaction probability \(p_{ij}^*\). Across several
samples each of several particles, this forms a distribution of
probabilities which are adjusted by the true and false negative rates.

@@

Why is this useful? For one, this analytic method avoids the extra
computation required by simulating samples from this distribution
directly. Further, it enables the extension of the natural analogue
between \(n_p\) (the number of particles) and the number of observations
of co-occurrence for a given pair of species---the fewer the particles,
the higher the variance of the resulting approximation. The normal
approximation is undefined for 0 particles (i.e.~0 observations
co-occurrence), although as \(n_p\) approaches 0 the approximated normal
(once truncated) approaches the uniform distribution on the interval
\((0,1)\), the maximum entropy distribution where we have no information
about the possibility of an interaction.
